---
title: "Weight of Fish"
author: "Dana Schroer"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)

Fish = read.csv("Fish.csv")
Perch = filter(Fish, Species == "Perch")
Pike = filter(Fish, Species == "Pike")
Roach = filter(Fish, Species == "Roach")
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```
## Perch
```{r}
Perchfullup <- lm(Weight~ .,data=Perch)
summary.lm(Perchfullup)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```


### Best Models
```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```
```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```
```{r}
anova(Perchfullup,best.model)
```
### Best Two regressor model
 The best regression model is the one with the highest adjusted r squared value and that is Height and Width and it has 2 regressors( but this isn't always the case) , so it is the model we're looking for.

## Pike
```{r}
Pikefullup <- lm(Weight~ .,data=Pike)
summary.lm(Pikefullup)
```
### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[5,]
```

```{r}
best.model <- lm(Weight~.,data=Perch)
summary(best.model)
```

### Best Two regressor model
The best model is the one that has Length1, Length2, Length3, Height and Width , because it has the highest adjusted r squared value. This means that all of these variables together affect the wight of the pike fish the most.

## Roach
```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Roach)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Roach,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```
```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```
### Best Models
Our best model is 4(1) because it fills the most categories filled.

### Best Two regressor model
the best model you can get using 2 models is length1 and length3

## Final Summary Statements
The best model at all times is 4(1) and the best 2 regresser for perch, pike and roach are length3 and height, length1 and length 3, and length1 and length 3 respectively.