---
title: "Weight of Fish"
author: "Dana Schroer"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)

Fish = read.csv("Fish.csv")
Perch = filter(Fish, Species == "Perch")
Pike = filter(Fish, Species == "Pike")
Roach = filter(Fish, Species == "Roach")
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```
## Perch
```{r}
Perchfullup <- lm(Weight~ .,data=Perch)
summary.lm(Perchfullup)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```


### Best Models
```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```
```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```
```{r}
anova(Perchfullup,best.model)
```
### Best Two regressor model
 The best regression model is the one with the highest adjusted r squared value and that is Height and Width and it has 2 regressors( but this isn't always the case) , so it is the model we're looking for.

## Pike
```{r}
Pikefullup <- lm(Weight~ .,data=Pike)
summary.lm(Pikefullup)
```
### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[5,]
```

```{r}
best.model <- lm(Weight~.,data=Perch)
summary(best.model)
```

### Best Two regressor model
The best model is the one that has Length1, Length2, Length3, Height and Width , because it has the highest adjusted r squared value. This means that all of these variables together affect the wight of the pike fish the most.

## Roach
```{r}
Roachfullup <- lm(Weight~ .,data=Roach)
summary.lm(Roachfullup)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomleft",main="Adjusted R^2")
```

```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[2,]
```

```{r}
best.model <- lm(Weight~Width+Length3,data=Roach)
summary(best.model)
```

```{r}
anova(Roachfullup,best.model)
```

### Best Two regressor model
The best regressor model is Length3 and Width, because it has the highest adjusted r squared value, so this means that the Length3 variable and Width variable( together ) affect the weight of the roaches the most.

## Final Summary Statements
We used a special test that can compare the relationship between the weight of the fish and the other characteristics of it like length, width, height....
We looked for the the model that had the highest adjusted r squared value and that model was the one that affected the weight of the fish the most.